\LARGE \bf Generalizing Informed Sampling for Asymptotically Optimal Sampling-based Kinodynamic Planning via Markov Chain Monte Carlo

### 2017-09-15 paper.tex
sync

\begin{figure}[tb]
  \centering
  	\includegraphics[trim={4.5cm 0 4cm 2cm},clip,height = 5.25cm ]{fig/alg.pdf}
  \caption{
    \captionstyle
  	Algorithmic approach.
  	Cost function is depicted using isocontours (darker shades reflect lower cost) while the boundary of the informed set is depicted in purple. 
  	The root-finding and MCMC algorithms are depicted in red and turquoise, respectively.
  	}
   	\label{fig:alg}
\end{figure}

@@

The idea behind applying MCMC for informed sampling is to define a target distribution~$ \pi $ as a uniform distribution over all points in~$ \Cinf $.
Our approach consists of two stages,
\begin{enumerate}
	\item finding an initial sample $ x_0 \in \Cinf $ which will serve as the start of a Markov chain. 
	This is implemented using the function 
	$ \texttt{sample\_in\_informed\_space}( )$, and
	\item sampling a new sample $ x_i \in \Cinf $ given a previous sample $ x_{i-1} $. 
	This is implemented using the function $\texttt{MCMC\_sample} (x_{i-1}, c_{\text{best}})$.
\end{enumerate}
Our algorithm is described in Alg.~\ref{alg:mcmc_informed_sampling} and visualized in Fig.~\ref{fig:alg}.
We now continue to detail each of the algorithm's stages.
%\os{Fix Alg 1 }

@@

\begin{algorithm}[t]
	\begin{algorithmic}[1]
		\STATE $ x'_{i} \leftarrow \texttt{sample\_normal}( q ( x \mid x_{i-1},\Sigma) ) $ 
		\label{start}
		\STATE $ \alpha \leftarrow \frac{ q ( x_{i-1} \mid x'_{i},\Sigma) \pi( x'_{i} ) }{ q ( x'_{i} \mid x_{i-1},\Sigma) \pi( x_{i-1} ) } $
		\IF{ \texttt{sample\_random}$ (0.0 , 1.0) > \min (1, \alpha) $  }
            \RETURN $ x'_{i} $
		\ENDIF
		\RETURN $ x_{i} $
	\end{algorithmic}
	\caption{Metropolis-Hastings MCMC $(x_{i-1}, c_{\text{best}})$}
	\label{alg:mh_mcmc}	
\end{algorithm}

@@

		\ENDLOOP
	\end{algorithmic}
	\caption{Hit-And-Run MCMC $(x_{i-1}, c_{\text{best}})$}
	\label{alg:hit_and_run_mcmc}	
\end{algorithm}

For this algorithm, we continue sampling along a Markov Chain until either 
(i)~the difference between the lower and upper bounds ($\lambda^-$ and $\lambda^+)$ 
that define our sampling domain is below a predefined threshold or
(ii)~a predefined number of samples was exceeded.
We want to point out that a Hit-and-Run sampler only requires that a Markov chain starts in an informed set, and will not produce a sample outside of the informed set.

@@

\begin{figure}[t!]
	\centering
	\begin{subfigure}[b]{\linewidth}
		\centering
		\includegraphics[width=.85\linewidth]{fig/sampling_efficiency/sample_efficiency_2d}
		\caption{\captionstyle 4-dimension sampling space.}
		\label{fig:sampling_efficiency:2d}
	\end{subfigure}
	\begin{subfigure}[b]{\linewidth}
		\centering
		\includegraphics[width=.85\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
		\caption{\captionstyle 12-dimension sampling space.}
		\label{fig:sampling_efficiency:6d}
	\end{subfigure}
	\caption{\captionstyle Average sampling time vs informed set volume ratio of four samplers (RS, HRS, MH and HNR) in state spaces of different dimensions. 
	The X axis is the ratio of informed set volume to the entire sampling space.
	The Y axis is the average time per sample.}
	\label{fig:sampling_efficiency}
\end{figure}

@@

\begin {table}[H]
\caption {Parameters for the problems} \label{tab:params} 
\begin{center}
	\begin{tabular}{c c c c c} 
\toprule
\multicolumn{2}{c}{Problem} & Position  & Velocity & $|acc_{max}|$ \\ [0.5ex] 
    &    &    $rad$       &  $rad/sec$    &  $rad/sec^2$ \\
\midrule
\multicolumn{2}{c}{3DoF Arm} & $[-\pi, \pi]$ & [-10, 10] & 1 \\ 
\midrule
\multicolumn{2}{c}{6DoF SnakeArm} & $[-\pi, \pi]$ & [-10, 10] & 1 \\
\midrule
\multirow{7}{*}{7DoF arm} & 1st & [0.541593 , 5.74159] & [-0.75, 0.75] & \multirow{7}{*}{1} \\
\cmidrule{2-4}            & 2nd &  [-2 , 2]            & [-0.75, 0.75]  &  \\
\cmidrule{2-4}            & 3rd & [-2.8, 2.8]          & [-2, 2] &  \\
\cmidrule{2-4}            & 4th & [-0.9, 3.1]          & [-2.5, 2.5] &  \\
\cmidrule{2-4}            & 5th & [-4.76, 1.24]        & [-2.5, 2.5] &  \\
\cmidrule{2-4}            & 6th & [-1.6, 1.6]          & [-2.5, 2.5] &  \\
\cmidrule{2-4}            & 7th & [-3, 3]              & [-2.5, 2.5] &  \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
\vspace{-2pt}

>>>>

\begin{figure}[tb]
  \centering
%  	\includegraphics[trim={4.5cm 0 4cm 2cm},clip,height = 5.25cm ]{fig/alg.pdf}
  	\includegraphics[width=0.75\linewidth ]{fig/alg.pdf}
  \caption{
    \captionstyle
  	Algorithmic approach.
  	Cost function is depicted using isocontours (darker shades reflect lower cost) while the boundary of the informed set is depicted in purple. 
  	The root-finding and MCMC algorithms are depicted in red and turquoise, respectively.
  	}
   	\label{fig:alg}
\end{figure}

@@

The idea behind applying MCMC for informed sampling is to define a target distribution~$ \pi $ that has $p(x_{sample}\in\Cinf) \ne 0 ~\&~ p(x_{sample})\notin\Cinf = 0$. 
This is specially useful if we want to bias the samples based on our knowledge of the environment.
However, we make no such assumption about the environment and use a uniform distribution over all points in~$ \Cinf $. 
Our approach consists of two stages,
\begin{enumerate}
	\item finding an initial sample $ x_0 \in \Cinf $ which will serve as the start of a Markov chain. 
	This is implemented using the function 
	$ \texttt{sample\_in\_informed\_space}( )$, and
	\item sampling a new sample $ x_i \in \Cinf $ given a previous sample $ x_{i-1} $. 
	This is implemented using the function $\texttt{MCMC\_sample} (x_{i-1}, c_{\text{best}})$.
\end{enumerate}
Our framework is described in Alg.~\ref{alg:mcmc_informed_sampling} and visualized in Fig.~\ref{fig:alg}.
We now continue to detail each of the algorithm's stages.
%\os{Fix Alg 1 }

@@

\begin{algorithm}[t]
	\begin{algorithmic}[1]
		\STATE $ x'_{i} \leftarrow \texttt{sample\_normal}( q ( x \mid x_{i-1},\Sigma) ) $ 
		\label{start}
		\STATE $ \alpha \leftarrow \frac{ q ( x_{i-1} \mid x'_{i},\Sigma) \pi( x'_{i} ) }{ q ( x'_{i} \mid x_{i-1},\Sigma) \pi( x_{i-1} ) } $
		\IF{ \texttt{sample\_random}$ (0.0 , 1.0) > \min (1, \alpha) $  }
            \RETURN $ x'_{i} $
		\ENDIF
		\RETURN $ x_{i} $
	\end{algorithmic}
	\caption{\captionstyle Metropolis-Hastings MCMC $(x_{i-1}, c_{\text{best}})$}
	\label{alg:mh_mcmc}	
\end{algorithm}

@@

		\ENDLOOP
	\end{algorithmic}
	\caption{\captionstyle Hit-And-Run MCMC $(x_{i-1}, c_{\text{best}})$}
	\label{alg:hit_and_run_mcmc}	
\end{algorithm}

For this algorithm, we continue sampling along a Markov Chain until either 
(i)~the difference between the lower and upper bounds ($\lambda^-$ and $\lambda^+)$ 
that define our sampling domain is below a predefined threshold or
(ii)~a predefined number of samples was exceeded.
We want to point out that a Hit-and-Run sampler only requires that a Markov chain starts in an informed set, and will not produce a sample outside of the informed set.
Also, in our implementation, we pick the start or the goal state to find $ x_0 \in \Cinf $ as the start of a Markov chain.

@@

\begin{figure}[t!]
	\centering
	\begin{subfigure}[b]{\linewidth}
		\centering
		\includegraphics[width=.70\linewidth]{fig/sampling_efficiency/sample_efficiency_2d}
		\caption{\captionstyle 4-dimension sampling space.}
		\label{fig:sampling_efficiency:2d}
	\end{subfigure}
	\begin{subfigure}[b]{\linewidth}
		\centering
		\includegraphics[width=.70\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
		\caption{\captionstyle 12-dimension sampling space.}
		\label{fig:sampling_efficiency:6d}
	\end{subfigure}
	\caption{\captionstyle Average sampling time vs informed set volume ratio of four samplers (RS, HRS, MH and HNR) in state spaces of different dimensions. 
	The X axis is the ratio of informed set volume to the entire sampling space.
	The Y axis is the average time per sample.}
	\label{fig:sampling_efficiency}
\end{figure}

@@

\begin {table}[H]
\caption {\captionstyle Parameters for the problems} \label{tab:params} 
\begin{center}
	\begin{tabular}{c c c c c} 
\toprule
\multicolumn{2}{c}{Problem} & Position  & Velocity & $|acc_{max}|$ \\ [0.5ex] 
    &    &    $rad$       &  $rad/sec$    &  $rad/sec^2$ \\
\midrule
\multicolumn{2}{c}{3DoF Arm} & $[-\pi, \pi]$ & [-10, 10] & 1 \\ 
\midrule
\multicolumn{2}{c}{6DoF SnakeArm} & $[-\pi, \pi]$ & [-10, 10] & 1 \\
\midrule
\multirow{7}{*}{7DoF arm} & 1st & [0.541593 , 5.74159] & [-0.75, 0.75] & \multirow{7}{*}{1} \\
\cmidrule{2-4}            & 2nd &  [-2 , 2]            & [-0.75, 0.75]  &  \\
\cmidrule{2-4}            & 3rd & [-2.8, 2.8]          & [-2, 2] &  \\
\cmidrule{2-4}            & 4th & [-0.9, 3.1]          & [-2.5, 2.5] &  \\
\cmidrule{2-4}            & 5th & [-4.76, 1.24]        & [-2.5, 2.5] &  \\
\cmidrule{2-4}            & 6th & [-1.6, 1.6]          & [-2.5, 2.5] &  \\
\cmidrule{2-4}            & 7th & [-3, 3]              & [-2.5, 2.5] &  \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
\vspace{-2pt}
